$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-05 paper/paper.tex
Comment on Arjen's work

Recent years have seen an increase in the efforts to mechanise resource-aware concurrency calculi, but the formalisation of the linear \picalc{} in Isabelle/HOL by Gay \cite{Gay2001} is perhaps one of the earliest works.
Gay encodes the \picalc{} with linear and shared types into a more general framework.
As we do, he uses de Bruijn indices, a reduction relation and a type system posterior to the syntax.
However, in his work context splits are explicit, and the types of used multiplicities erased.

@@

\cite{Rouvoet2020}

>>>>

Recent years have seen an increase in the efforts to mechanise resource-aware concurrency calculi, but perhaps one of the earliest works is the formalisation of the linear \picalc{} in Isabelle/HOL by Gay \cite{Gay2001}.
Gay encodes the \picalc{} with linear and shared types into a more general framework.
As we do, he uses de Bruijn indices, a reduction relation and a type system posterior to the syntax.
However, in his work context splits are explicit, and the types of used multiplicities erased.

@@

Most recently, Rouvoet et al. provide an intrinsic encoding (where type safety follows by construction) of a \lambdacalc{} with session types \cite{Rouvoet2020}.
They use proof relevant separation logic and a notion of a supply and demand \emph{market} to make context splits transparent to the user.
Their separation logic is based on a partial commutative monoid that need not be functional nor cancellative.
Their typing rules preserve the balance between supply and demand, and are very elegant.
They distill their typing rules even further by modelling the supply and demand market as a state monad.
